---
title: "Introduction-to-fargh"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction-to-fargh}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fargh)
```



The goal of fargh is to offer tools to report and analyse accidents
reports over years.The fargh package provides functions to read,
summarize and visualize data on accidents recorded by time, date,
geographical information such as: city, state, longitude, latitude… and
more.

You can download and install the development version of fargh using:

  devtools::install_github("Quan-Cui/fargh", build_vignettes = TRUE)

You can prepare the example csv data included using in the following way:

```{r download data}
make_filename(2013)
make_filename(2014)
make_filename(2015)
readr::write_csv(accident_2013.csv.bz2, "accident_2013.csv.bz2")

readr::write_csv(accident_2014.csv.bz2, "accident_2014.csv.bz2")

readr::write_csv(accident_2015.csv.bz2, "accident_2015.csv.bz2")
```


